Breakable Elastic-plastic Constraint for\\Rigid Body Simulation

### 2017-10-09 pdocs/thesis/epj-jcgt.tex
work on jcgt article

@@

\subsection{Examples}

\paragraph{Cantilever beam}

\paragraph{Multifloor frame}

\paragraph{Car} 
Dynamic bodies are car (680 kg), wheels (50 kg for each axel), and ramp (2160 kg). 
Ramp is joined to fixed part with b2ElasticPlasticJoint having frequency of 1 Hz.
Maximum elastic rotation is set to 0.12 and maximum plastic rotation to 0.4.
With this configuration own weight or ramp uses about 13 \% of plastic capacity.
After first jump about 50 \% of  plastic capacity is used. Each additional jump uses about 
7 \% of plastic capacity.

>>>>

\paragraph{Joint breaking in one simulation step} High velocity collisions may cause joints to break within one step.
In such cases joints can cause too large impulse. Making simulation step smaller is not desired solution.
In this paper following procedure is suggested.

\begin{enumerate}
\item 
\end{enumerate}

@@

\section{Examples}

\subsection{Cantilever beam}

\subsection{Multifloor frame}

\subsection{Car} 
Dynamic bodies are car (680 kg), wheels (50 kg for each axel), and ramp (2160 kg). 
Ramp is joined to fixed part with b2ElasticPlasticJoint having frequency of 1 Hz.
Maximum elastic rotation is set to 0.12 and maximum plastic rotation to 0.4.
With this configuration own weight or ramp uses about 13 \% of plastic capacity.
After first jump about 50 \% of  plastic capacity is used. Each additional jump uses about 
7 \% of plastic capacity.
